---
title: "Analysis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: flatly
    number_sections: true
    toc: true
    toc_float: true
---

# Análisis PPM-S

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "analysis-cfa.Rmd",output_format = "html_document")
```

```{r}
library(sjPlot)
library(dplyr)
library(lavaan)

data01 <- sjlabelled::read_spss(path = "data/Estudio_3_ola1_January_9_2020.sav",verbose = FALSE)

dat01 <- data01 %>% filter(Intro==1) %>% select(starts_with("meritv01")) %>% na.omit()
dat02 <- data01 %>% filter(Intro==1) %>% select(starts_with("meritv02")) %>% na.omit()
dat03 <- data01 %>% filter(Intro==1) %>% select(starts_with("meritv03_p")) %>% na.omit()

```

## Version 01: Fixed order by perception / preferences (N=  )

1. Percepcion esfuerzo
2. Percepcion talento
3. Percepcion familia rica
4. Percepcion redes
5. Preferencia esfuerzo
6. Preferencia talento
7. Preferencia familia rica
8. Preferencia redes


```{r,results='hold'}
model01 <- 'perc_merit=~meritv01_perc_effort+meritv01_perc_talent 
            perc_nmerit=~meritv01_perc_wpart+meritv01_perc_netw  
            pref_merit=~meritv01_pref_effort+meritv01_pref_talent 
            pref_nmerit=~meritv01_pref_wpart+meritv01_pref_netw'

fit1 <- cfa(model = model01,data = dat01,ordered = c("meritv01_perc_effort","meritv01_perc_talent",
                                                     "meritv01_perc_wpart","meritv01_perc_netw",
                                                     "meritv01_pref_effort","meritv01_pref_talent",
                                                     "meritv01_pref_wpart","meritv01_pref_netw"))

summary(fit1,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit1,what = "std",thresholds = FALSE, intercepts = FALSE)
```

*summary*: good fit, heywood case item 8.

## Version 02: Fixed order, by topic (N=  )

1. Percepcion esfuerzo
2. Preferencia esfuerzo
3. Percepcion talento
4. Preferencia talento
5. Percepcion familia rica
6. Preferencia familia rica
7. Percepcion redes
8. Preferencia redes

```{r,results='hold'}
model02 <- 'perc_merit=~meritv02_perc_effort+meritv02_perc_talent 
            perc_nmerit=~meritv02_perc_wpart+meritv02_perc_netw  
            pref_merit=~meritv02_pref_effort+meritv02_pref_talent 
            pref_nmerit=~meritv02_pref_wpart+meritv02_pref_netw'

fit2 <- cfa(model = model02,data = dat02,ordered = c("meritv02_perc_effort","meritv02_perc_talent",
                                                     "meritv02_perc_wpart","meritv02_perc_netw",
                                                     "meritv02_pref_effort","meritv02_pref_talent",
                                                     "meritv02_pref_wpart","meritv02_pref_netw"))

summary(fit2,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit2,what = "std")
```
*summary*: bad fit, heywood 

## Version 03: Random order

```{r,results='hold'}
model03 <- 'perc_merit=~meritv03_perc_effort+meritv03_perc_talent 
            perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw  
            pref_merit=~meritv03_pref_effort+meritv03_pref_talent 
            pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw'

fit3 <- cfa(model = model03,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                     "meritv03_perc_wpart","meritv03_perc_netw",
                                                     "meritv03_pref_effort","meritv03_pref_talent",
                                                     "meritv03_pref_wpart","meritv03_pref_netw"))

summary(fit3,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit3,what = "std",thresholds = FALSE, intercepts = FALSE)
```

*summary*: fit not very goood (RMSEA .7), no heywood. Try tau-equivalence

## Version 04: muestra completa (N=  )


```{r,results='hold'}
dat04 <- data01 %>% filter(Intro==1) %>% select(starts_with("meritv01"),starts_with("meritv02"),starts_with("meritv03_p"))

dat04$perc_effort <- rowSums(dat04[,c(matches(match = "perc_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_talent <- rowSums(dat04[,c(matches(match = "perc_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_wpart  <- rowSums(dat04[,c(matches(match = "perc_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$perc_netw   <- rowSums(dat04[,c(matches(match = "perc_netw"  ,vars = names(dat04)))],na.rm = TRUE)

dat04$pref_effort <- rowSums(dat04[,c(matches(match = "pref_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_talent <- rowSums(dat04[,c(matches(match = "pref_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_wpart  <- rowSums(dat04[,c(matches(match = "pref_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$pref_netw   <- rowSums(dat04[,c(matches(match = "pref_netw"  ,vars = names(dat04)))],na.rm = TRUE)

model04 <- 'perc_merit=~perc_effort+perc_talent 
            perc_nmerit=~perc_wpart+perc_netw  
            pref_merit=~pref_effort+pref_talent 
            pref_nmerit=~pref_wpart+pref_netw'

fit4 <- cfa(model = model04,data = dat04)
summary(fit4,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit4,what = "std",thresholds = FALSE, intercepts = FALSE)
```

