---
title: "Data preparation Study 2 - Merit Scale"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/bib/style.css"
output:
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "hide"
editor_options:
  chunk_output_type: console
---


```{r include=FALSE}
# Knitr options

knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE,results = "hold")
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

This is the preparation code of the data for Study 2,: the Perceptions and Preferences of Meritocracy Scale. The prepared data is `data_s2.RData`

# Libraries
```{r}
pacman::p_load(sjmisc, sjPlot, dplyr, tidyr, lavaan, stargazer, corrplot, psych, knitr, kableExtra, summarytools, sjlabelled, Hmisc)
```

# Load original data

```{r}
data <- sjlabelled::read_spss("input/data/original/Estudio_3_ola1.sav",verbose = F)
dim(data)
```

# Select variables subset

First we select those who that accepted to participate in the informed consent based on the response to the variable `Intro`:

```{r}
table(data$Intro)
```

There are 2236 who accepted to participate (1) and 221 who does not (221). Now we filter them:

```{r}
data_s2 <- data %>% filter(Intro==1)
```

Now we select the variables of the scale which are the ones with "meritv0" in the label are the ones used in the scale (8 items):

```{r}
find_var(data = data_s2,"meritv03")
```

There are 4 topics (effort, talents, parents' wealth & networks) both for perceptions and preferences, summing up 8 items in total.

Suffixes v01, v02 & v03 make reference to the different order sets in which items were administrated (see paper for more details). Besides, we select variables that indicate the order set, beggining with FL_21_DO


```{r}
data_s2 <- data_s2 %>%
  select(starts_with("meritv01"),
         starts_with("meritv02"),
         starts_with("meritv03"),
         starts_with("FL_21_DO"))

dim(data_s2)
sjmisc::descr(data_s2, show = "short") # labels too long: shorten

```

Change long labels from FL_21 ... variables

```{r}
data_s2 <- data_s2 %>% rename(
  "id_v1"=FL_21_DO_merit_perc_pref_julio19v01,
  "id_v2"=FL_21_DO_merit_perc_pref_julio19v02,
  "id_v3"=FL_21_DO_merit_perc_pref_julio19v03
  )
```

# Process variables for analysis

In the following we make a unique identification for each item across order sets, and create a variable that allows identifying to which administration set they belong.

First just check whether the set's id variables are working properly identifying the corresponding items:

```{r}
data_s2 %>% filter(id_v1==1) %>%sjmisc::descr(., show = "short")
data_s2 %>% filter(id_v2==1) %>%sjmisc::descr(., show = "short")
data_s2 %>% filter(id_v3==1) %>%sjmisc::descr(., show = "short")
```

Ok. Now recode de values on the version in order to be able to identify the groups afterwards

```{r}
data_s2$id_v2 <- car::recode(data_s2$id_v2, "1=2")
data_s2$id_v3 <- car::recode(data_s2$id_v3, "1=3")

```

Now we create the variables across response set versions. For this first we create a vector with the corresponding variable names, e.g. the three containing "perc_effort" (independent of the ser version). Then we use these vectors for creating the new variables with `coalesce`.


```{r}
#create vector with names
match_perc_effort = rlang::syms(grep("perc_effort", names(data_s2), value = TRUE))
match_perc_talent = rlang::syms(grep("perc_talent", names(data_s2), value = TRUE))
match_perc_wpart = rlang::syms(grep("perc_wpart", names(data_s2), value = TRUE))
match_perc_netw = rlang::syms(grep("perc_netw", names(data_s2), value = TRUE))
match_pref_effort = rlang::syms(grep("pref_effort", names(data_s2), value = TRUE))
match_pref_talent = rlang::syms(grep("pref_talent", names(data_s2), value = TRUE))
match_pref_wpart = rlang::syms(grep("pref_wpart", names(data_s2), value = TRUE))
match_pref_netw = rlang::syms(grep("pref_netw", names(data_s2), value = TRUE))
match_set_version = rlang::syms(grep("id_v", names(data_s2), value = TRUE))

#create variables
data_s2 <- data_s2 %>%
  mutate(perc_effort = coalesce(!!! match_perc_effort),
         perc_talent = coalesce(!!! match_perc_talent),
         perc_wpart = coalesce(!!! match_perc_wpart),
         perc_netw = coalesce(!!! match_perc_netw),
         pref_effort = coalesce(!!! match_pref_effort),
         pref_talent = coalesce(!!! match_pref_talent),
         pref_wpart = coalesce(!!! match_pref_wpart),
         pref_netw = coalesce(!!! match_pref_netw),
         group = coalesce(!!! match_set_version)
        )

#check:
data_s2 %>% select(perc_effort, meritv01_perc_effort, meritv02_perc_effort, meritv03_perc_effort) %>% slice_head(n=10)

sjmisc::descr(data_s2)
frq(data_s2$group)

# 75 NAs in group, probably those who not continued the survey, check:

data_s2 %>%  filter(is.na(group))

# Ok, remove NAs in groups

data_s2 <- data_s2 %>%  filter(!is.na(group))
```

Now select the final variables

```{r}
data_s2 <- data_s2 %>% select(perc_effort,perc_talent,perc_wpart, perc_netw,
                              pref_effort,pref_talent,pref_wpart, pref_netw,
                              group)

names(data_s2)
dim(data_s2)
```


## Labels

### Variable labels

```{r}

set_label(data_s2$group) <- "Order sets"

set_label(data_s2$perc_effort)  <- "More effort get greater rewards"
set_label(data_s2$perc_talent)  <- "More talent get greater rewards"
set_label(data_s2$perc_wpart)   <- "Rich parents to get ahead"
set_label(data_s2$perc_netw)    <- "Contacts to get ahead"

set_label(data_s2$pref_effort)  <- "More effort should get greater rewards"
set_label(data_s2$pref_talent)  <- "More talent should get greater rewards"
set_label(data_s2$pref_wpart)   <- "Rich parents should get ahead"
set_label(data_s2$pref_netw)    <- "Contacts should get ahead"

sjmisc::descr(data_s2)
sjmisc::frq(data_s2$perc_effort)

```

### Value labels
```{r}
get_labels(data_s2$perc_effort) # translate

# generate vector of variables to relabel:
perc_or_pref = rlang::syms(grep("perc_|pref_", names(data_s2), value = TRUE))
perc_or_pref


# label values

data_s2 <- data_s2  %>% replace_labels(labels = c("Strongly disagree" = 1, "Disagree" = 2, "Neither agree nor disagree"=3,"Agree"=4, "Totally agree" = 5))

data_s2$group<- set_labels(data_s2$group, labels = c("Order set 1"=1,"Order set 2"=2,"Order set 3"=3 ))


#check
get_labels(data_s2$perc_effort) # ok
get_labels(data_s2$group) # ok

sjmisc::descr(data_s2)

```

# Final summary
```{r}
sjmisc::descr(data_s2,
      show = c("label","range", "mean", "sd", "NA.prc", "n"))%>%
      kable(.,"markdown")

print(dfSummary(data_s2, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")

```


## save data

```{r}

save(data_s2,file = "input/data/proc/data_s2.RData")
```
