---
title: "Analysis PPM-S"
date: "`r format(Sys.time(), '%d %B, %Y')`"
css: "../input/bib/style.css"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: "hide"
editor_options: 
  chunk_output_type: console
---

This section, documents all the procedures related to the data analysis and measurement models.
(description)




# Wave 01 {.tabset .tabset-fade .tabset-pills}

Design: this wave ....

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_analysis-cfa.Rmd",output_format = "html_document")
```

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

**Libraries**
```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
```

**Load data**
```{r}
data01 <- sjlabelled::read_spss(path = "input/data/original/Estudio_3_ola1.sav",verbose = FALSE)

dat01 <- data01 %>% filter(Intro==1,Finished==1) %>% select(starts_with("meritv01"))   %>% na.omit()
dat02 <- data01 %>% filter(Intro==1,Finished==1) %>% select(starts_with("meritv02"))   %>% na.omit()
dat03 <- data01 %>% filter(Intro==1,Finished==1) %>% select(starts_with("meritv03_p")) %>% na.omit()

# - Nos quedamos solamente con los casos que ACEPTARON participar y terminaron el cuestionario.
# - Para dejar una base que contenga solamente los casos que tienen información completa en los ítems usamos na.omit()

dat04 <- data01 %>% filter(Intro==1) %>%
  select(starts_with("meritv01"),
         starts_with("meritv02"),
         starts_with("meritv03_p"),
         starts_with("FL_21_DO")) 
dat04$grupo <- NA
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v01==1] <- 1
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v02==1] <- 2
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v03==1] <- 3
dat04$perc_effort <- rowSums(dat04[,c(matches(match = "perc_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_talent <- rowSums(dat04[,c(matches(match = "perc_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_wpart  <- rowSums(dat04[,c(matches(match = "perc_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$perc_netw   <- rowSums(dat04[,c(matches(match = "perc_netw"  ,vars = names(dat04)))],na.rm = TRUE)

dat04$pref_effort <- rowSums(dat04[,c(matches(match = "pref_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_talent <- rowSums(dat04[,c(matches(match = "pref_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_wpart  <- rowSums(dat04[,c(matches(match = "pref_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$pref_netw   <- rowSums(dat04[,c(matches(match = "pref_netw"  ,vars = names(dat04)))],na.rm = TRUE)
dat04[dat04==0] <- NA
```

---

**Modality**

Each group correspond to the application modality of the scale. 

1. **Version 01:** Fixed order by perception / preferences (N=`r dim(dat01)[1]`)

2. **Version 02:** Fixed order, by topic (N=`r dim(dat02)[1]`)

3.  **Version 03:** Random order (N=`r dim(dat03)[1]`)

4. **Complete Sample:** Complete sample (N=`r dim(dat04)[1]`)

## Version 01 (N=`r dim(dat01)[1]`){.tabset}

| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| 1. Percepción esfuerzo      | Perception effort      |
| 2. Percepción talento       | Perception talent      |
| 3. Percepción familia rica  | Perception rich family |
| 4. Percepción redes         | Perception networks    |
| 5. Preferencia esfuerzo     | Preference effort      |
| 6. Preferencia talento      | Preference talent      |
| 7. Preferencia familia rica | Preference rich family |
| 8. Preferencia redes        | Preference networks    |
Table: Mode 01: Fixed order by perception  

```{r echo=FALSE,results='asis'}
stargazer(dat01,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort", "2. pc.talent","3. pc.wpart","4. pc.netw","5. pf.effort","6. pf.talent","7. pf.wpart", "8. pf.netw"))




```

```{r correlacion v01}
cor01<-polychoric(dat01)
rownames(cor01$rho) <- c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor01$rho) <- c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor01$rho,method = "color" ,type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r}
model01 <- 'perc_merit=~meritv01_perc_effort+meritv01_perc_talent
            perc_nmerit=~meritv01_perc_wpart+meritv01_perc_netw
            pref_merit=~meritv01_pref_effort+meritv01_pref_talent
            pref_nmerit=~meritv01_pref_wpart+meritv01_pref_netw'

fit1_c <- cfa(model = model01,data = dat01,estimator="MLR") # Continuous/ estimator ML Robust

fit1_o <- cfa(model = model01,data = dat01,
            ordered = c("meritv01_perc_effort","meritv01_perc_talent",
                        "meritv01_perc_wpart","meritv01_perc_netw",
                        "meritv01_pref_effort","meritv01_pref_talent",
                        "meritv01_pref_wpart","meritv01_pref_netw"))

#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit1_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit1_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```

> **NOTE**: good fit, heywood case item 8.

## Version 02  (N=`r dim(dat02)[1]`)

| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| 1. Percepción esfuerzo      | Perception effort      |
| 2. Preferencia esfuerzo     | Preference effort      |
| 3. Percepción talento       | Perception talent      |
| 4. Preferencia talento      | Preference talent      |
| 5. Percepción familia rica  | Perception rich family |
| 6. Preferencia familia rica | Preference rich family |
| 7. Percepción redes         | Perception networks    |
| 8. Preferencia redes        | Preference networks    |
Table: Mode 02: Fixed order, by topic.

```{r echo=FALSE,results='asis'}
stargazer(dat02,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort","2. pf.effort","3. pc.talent","4. pf.talent","5. pc.wpart","6. pf.wpart","7. pc.netw","8 pc.netw"))
```

```{r}
cor02<-polychoric(dat02)
rownames(cor02$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor02$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor02$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```


```{r,results='hold'}
model02 <- 'perc_merit=~meritv02_perc_effort+meritv02_perc_talent
            perc_nmerit=~meritv02_perc_wpart+meritv02_perc_netw
            pref_merit=~meritv02_pref_effort+meritv02_pref_talent
            pref_nmerit=~meritv02_pref_wpart+meritv02_pref_netw'

fit2_c <- cfa(model = model02,data = dat02,estimator="MLR") # Continuous/ estimator ML Robust

fit2_o <- cfa(model = model02,data = dat02,ordered = c("meritv02_perc_effort","meritv02_perc_talent",
                                                       "meritv02_perc_wpart"  ,"meritv02_perc_netw",
                                                       "meritv02_pref_effort" ,"meritv02_pref_talent",
                                                       "meritv02_pref_wpart"  ,"meritv02_pref_netw"))

#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit2_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit2_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```
> **NOTE**: bad fit, heywood case using DWLS

## Version 03 (N=`r dim(dat03)[1]`)


| Spanish (original)          | English (translated)   |
|-----------------------------|------------------------|
| Orden aleatorio             | Randomized order       |

Table: Mode 03: Randomized order.

```{r echo=FALSE,results='asis'}
stargazer(dat03,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort", "2. pc.talent","3. pc.wpart","4. pc.netw","5. pf.effort","6. pf.talent","7. pf.wpart", "8. pf.netw"))
```

```{r}
cor03<-polychoric(dat03)
rownames(cor03$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor03$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor03$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model03 <- '
perc_merit=~meritv03_perc_effort+meritv03_perc_talent 
perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw  
pref_merit=~meritv03_pref_effort+meritv03_pref_talent 
pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw'

fit3_c <- cfa(model = model03,data = dat03,estimator="MLR",std.lv=FALSE) # Continuous/ estimator ML Robust

fit3_o <- cfa(model = model03,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                       "meritv03_perc_wpart","meritv03_perc_netw",
                                                       "meritv03_pref_effort","meritv03_pref_talent",
                                                       "meritv03_pref_wpart","meritv03_pref_netw"),std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit3_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit3_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```

> **NOTE**: fit not very goood (RMSEA .7), no heywood. Try tau-equivalence

### Tau-equivalence

```{r,results='hold'}
model03.tau <- '
perc_merit=~ r1*meritv03_perc_effort+r1*meritv03_perc_talent 
perc_nmerit=~r2*meritv03_perc_wpart+ r2*meritv03_perc_netw  
pref_merit=~ r3*meritv03_pref_effort+r3*meritv03_pref_talent 
pref_nmerit=~r4*meritv03_pref_wpart+ r4*meritv03_pref_netw'

fit3_c.tau <- cfa(model = model03.tau,data = dat03,estimator="MLR",std.lv=FALSE) # Continuous/ estimator ML Robust

fit3_o.tau <- cfa(model = model03.tau,data = dat03,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                               "meritv03_perc_wpart","meritv03_perc_netw",
                                                               "meritv03_pref_effort","meritv03_pref_talent",
                                                               "meritv03_pref_wpart","meritv03_pref_netw"), std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit3_c.tau ) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit3_o.tau) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

```{r}
kable(rbind(Ordinal    =fitmeasures(fit3_o    )[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal.tau=fitmeasures(fit3_o.tau)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",
      digits = 3, caption = "Fit tau-equivalence")
kable(anova(fit3_o,fit3_o.tau),
      format = "markdown",
      digits = 3)
```

<!-- > **NOTE:** El modelo con igualdad de cargas factoriales (en Percepción meritocracia) no deteriora significativamente el ajuste del modelo. -->

> **NOTE:** The model with equal factor loadings (in Meritocracy Perception) does not significantly deteriorate the model fit.

## Complete sample (N=`r dim(dat04)[1]`)

| Spanish (original)                           | English (translated)                 |
|----------------------------------------------|--------------------------------------|
| Orden fijo, según percepción/preferencia     | Fixed order, by perception/preference|
| Orden fijo, por tópico                       | Fixed order, by topic.               |
| Orden aleatorizado                           | Randomized order                     |
Table: Mode 04: Complete sample

```{r echo=FALSE,results='asis'}
stargazer(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw),
          type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2,
          covariate.labels = c("1. pc.effort", "2. pc.talent","3. pc.wpart","4. pc.netw","5. pf.effort","6. pf.talent","7. pf.wpart", "8. pf.netw"))
```

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
rownames(cor04$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor04$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model04 <- '
perc_merit =~ perc_effort+perc_talent 
perc_nmerit=~perc_wpart +perc_netw  
pref_merit =~ pref_effort+pref_talent 
pref_nmerit=~pref_wpart +pref_netw'

fit4_c <- cfa(model = model04,data = dat04,estimator="MLR",std.lv=FALSE) # Continuous/ estimator ML Robust

fit4_o <- cfa(model = model04,data = dat04,ordered = c("perc_effort","perc_talent",
                                                       "perc_wpart","perc_netw",
                                                       "pref_effort","pref_talent",
                                                       "pref_wpart","pref_netw"),std.lv=FALSE)
#---------------------------------------------------#
cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit4_c ) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),y = standardizedsolution(fit4_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames, caption = "Factor loadings")
```

# Summary fit indices wave 01

```{r}
sum_fit<- bind_rows(fitmeasures(fit1_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit1_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit2_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit3_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                    fitmeasures(fit4_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])
sum_fit$mod <- c("Model 1","Model 1","Model 2","Model 2","Model 3","Model 3","Model 4","Model 4")
sum_fit$est <- c("Continous","Ordinal","Continous","Ordinal","Continous","Ordinal","Continous","Ordinal")
sum_fit <- select(sum_fit,mod,est,everything())

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 01") %>%     kable_styling(full_width = F)  %>% 
      collapse_rows(columns = 1,valign = "middle")  %>%  
      footnote(number = c("Model 1: fixed order by percepction/preference", 
                          "Model 2: fixed order by topic (i.e: effort)", 
                          "Model 3: Randomized order",
                          "Model 4: Complete sample"));sumtable01 

# Save sumamry table wave 01------------------------------#
# as_image(sumtable01,file = "output/sumtablew01.png")
save_kable(sumtable01,file = "output/tables/sumtablew01.html",self_contained = FALSE)
```

## Other analyses

### Multigroup CFA

* The group specification correspond to the application modality of the scale.

```{r}
model04 <- '
perc_merit =~ perc_effort+perc_talent 
perc_nmerit=~perc_wpart +perc_netw  
pref_merit =~ pref_effort+pref_talent 
pref_nmerit=~pref_wpart +pref_netw'

fit4_c_mg <- cfa(model = model04,data = dat04,estimator="MLR",std.lv=FALSE,group = "grupo") # Continuous/ estimator ML Robust
fit4_o_mg <- cfa(model = model04,data = dat04,ordered = c("perc_effort","perc_talent",
                                                          "perc_wpart","perc_netw",
                                                          "pref_effort","pref_talent",
                                                          "pref_wpart","pref_netw"),std.lv=FALSE, group = "grupo")
#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fit4_c_mg)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal=  fitmeasures(fit4_o_mg)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3,caption = "Fit indices")

cnames <- c("Grupo","Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit4_c_mg) %>% filter(op=="=~") %>% select(group,lhs,rhs,est.std),
                y = standardizedsolution(fit4_o_mg) %>% filter(op=="=~") %>% select(group,lhs,rhs,est.std),
                c("group","lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames,caption = "Factor loadings by group")
```

### Second order CFA

#### SO-CFA Perception and Preference

```{r}
model04b1or <- '
perc_merit=~ perc_effort+perc_talent 
perc_nmerit=~perc_wpart +perc_netw  
pref_merit=~ pref_effort+pref_talent 
pref_nmerit=~pref_wpart +pref_netw
percep=~ perc_merit + perc_nmerit
prefer=~ pref_merit + pref_nmerit'

fit4a_c <- cfa(model = model04b1or,data = dat04, estimator="MLR")

fit4b_c <- cfa(model = model04b1or,data = dat04,ordered = c("perc_effort","perc_talent","perc_wpart","perc_netw",
                                                            "pref_effort","pref_talent","pref_wpart","pref_netw"))

#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fit4a_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal= fitmeasures(fit4b_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit4a_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                y = standardizedsolution(fit4b_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames,caption = "Factor loadings")
```

<!-- > **NOTE:** Cargas factoriales de segundo orden son bajas. El ajuste del modelo no es bueno. -->

> **NOTE:** Second order factor loads are low. The fit of the model is not good.

#### SO-CFA Meritocratic y Non-meritocratic

```{r}
model04b2or <-'perc_merit=~ perc_effort+perc_talent
               perc_nmerit=~perc_wpart +perc_netw
               pref_merit=~ pref_effort+pref_talent
               pref_nmerit=~pref_wpart +pref_netw
               merit =~ perc_merit  + pref_merit
               nmerit=~ perc_nmerit + pref_nmerit'

# fit4b_c <- cfa(model = model04b2or,data = dat04,estimator="MLR") # No converge

fit4b_o <- cfa(model = model04b2or,data = dat04, 
               ordered = c("perc_effort","perc_talent","perc_wpart","perc_netw",
                           "pref_effort","pref_talent","pref_wpart","pref_netw"))

#---------------------------------------------------#
kable(rbind(Ordinal=fitmeasures(fit4b_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (DWLS)")
kable(standardizedsolution(fit4b_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
      format = "markdown",digits = 2,col.names = cnames,caption = "Factor loadings")
```

<!-- > **NOTE:** El modelo estimado con MLR con factores de segundo orden "meritocracia/ no meritocracia" no converge. EL modelo estimado a través de DWLS converge, posee cargas muy bajas y una muy alta (merit~pref_merit). Fit es malo (RMSEA >.10) -->

> **NOTE:**  The model estimated with MLR with second order factors "meritocracy / non meritocracy" does not converge. The model estimated through DWLS converges, has very low loads and a very high one (merit ~ pref_merit). Fit is bad (RMSEA> .10)


# Wave 02 {.tabset .tabset-fade .tabset-pills}


Each sample correspond to one of the three conditions generated by the randomized assignment. 

1. **Control group:** the group that has been assigned to the control group (placebo condition)

2. **Poverty condition sample** the group that has been assigned to the Poverty treatment condition. 

3. **Inequality condition sample:** the group that has been assigned to the Inequality treatment condition.

4. **Complete sample:** Control, Poverty and Inequality treatment.


```{r}
data02 <- sjlabelled::read_spss(path = "input/data/original/Estudio_3_ola2.sav",verbose = FALSE)
load(file = "input/data/proc/datawide.RData")
dat01 <- data02 %>% select(starts_with("meritv03_p")) 
```

**ATE on observed indicators**

```{r, out.width="75%",results='asis'}
m01<- lm(perc_effort_w2~treat,data = wide01)
m02<- lm(perc_talent_w2~treat,data = wide01)
m03<- lm(perc_wpart_w2~treat, data = wide01)
m04<- lm(perc_netw_w2~treat,  data = wide01)
#--------------------------------------------#
m05<- lm(pref_effort_w2~treat,data = wide01)
m06<- lm(pref_talent_w2~treat,data = wide01)
m07<- lm(pref_wpart_w2 ~treat, data = wide01)
m08<- lm(pref_netw_w2  ~treat,  data = wide01)
#--------------------------------------------#
stargazer::stargazer(m01,m02,m03,m04,type = "html")
stargazer::stargazer(m05,m06,m07,m08,type = "html")
```

<!-- > **NOTE**: Los tratamientos de información no se asocian de manera estadísticamente significativa con ninguno de los Indicatores de la escala de meritocracia.   -->

> **NOTE**: There are no statistically significant effects of the treatment conditions on the observed indicators of the meritocracy scale. 


## Control group

```{r}
w02con <- data02 %>% filter(FL_6_DO_Control==1) %>% select(starts_with("meritv03_p")) 
```

```{r echo=FALSE,results='asis'}
stargazer(w02con,type = "html",          
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

```{r}
corw02_1<-polychoric(w02con)
rownames(corw02_1$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(corw02_1$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(corw02_1$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```


```{r,results='hold'}
model03 <- '
perc_merit=~meritv03_perc_effort+meritv03_perc_talent 
perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw  
pref_merit=~meritv03_pref_effort+meritv03_pref_talent 
pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw'

fitw02a_c <- cfa(model = model03,data = w02con,estimator="MLR") # Continuous/ estimator ML Robust

fitw02a_o <- cfa(model = model03,data = w02con,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                           "meritv03_perc_wpart","meritv03_perc_netw",
                                                           "meritv03_pref_effort","meritv03_pref_talent",
                                                           "meritv03_pref_wpart","meritv03_pref_netw"))
#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fitw02a_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal= fitmeasures(fitw02a_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fitw02a_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                y = standardizedsolution(fitw02a_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

## Poverty condition

```{r}
w02pob <- data02 %>% filter(FL_6_DO_Tratamiento==1) %>% select(starts_with("meritv03_p")) 
```

```{r echo=FALSE,results='asis'}
stargazer(w02pob,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

```{r}
corw02_2<-polychoric(w02pob)
rownames(corw02_2$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(corw02_2$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(corw02_2$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model03 <- '
perc_merit=~meritv03_perc_effort+meritv03_perc_talent 
perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw  
pref_merit=~meritv03_pref_effort+meritv03_pref_talent 
pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw'

fitw02b_c <- cfa(model = model03,data = w02pob,estimator="MLR") # Continuous/ estimator ML Robust

fitw02b_o <- cfa(model = model03,data = w02pob,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                           "meritv03_perc_wpart","meritv03_perc_netw",
                                                           "meritv03_pref_effort","meritv03_pref_talent",
                                                           "meritv03_pref_wpart","meritv03_pref_netw"))

#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fitw02b_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal= fitmeasures(fitw02b_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fitw02b_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                y = standardizedsolution(fitw02b_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

## Inequality condition 

```{r}
w02des <- data02 %>% filter(FL_6_DO_Tratamiento_desigualdad==1) %>% select(starts_with("meritv03_p")) 
```

```{r echo=FALSE,results='asis'}
stargazer(w02des,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

```{r}
corw02_3<-polychoric(w02des)
rownames(corw02_3$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(corw02_3$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(corw02_3$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model03 <- '
perc_merit=~meritv03_perc_effort+meritv03_perc_talent
perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw  
pref_merit=~meritv03_pref_effort+meritv03_pref_talent 
pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw'

fitw02c_c <- cfa(model = model03,data = w02des,estimator="MLR") # Continuous/ estimator ML Robust

fitw02c_o <- cfa(model = model03,data = w02des,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                           "meritv03_perc_wpart","meritv03_perc_netw",
                                                           "meritv03_pref_effort","meritv03_pref_talent",
                                                           "meritv03_pref_wpart","meritv03_pref_netw"))
#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fitw02c_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal= fitmeasures(fitw02c_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fitw02c_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                y = standardizedsolution(fitw02c_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

## Complete sample

```{r echo=TRUE,results='asis'}
stargazer(dat01,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

```{r}
dat01cor<- select(dat01,meritv03_perc_effort,meritv03_perc_talent,
                        meritv03_perc_wpart,meritv03_perc_netw,
                        meritv03_pref_effort,meritv03_pref_talent,
                        meritv03_pref_wpart,meritv03_pref_netw)
cor01<-polychoric(dat01cor)
rownames(cor01$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(cor01$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(cor01$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model03 <- '
perc_merit=~meritv03_perc_effort+meritv03_perc_talent 
perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw  
pref_merit=~meritv03_pref_effort+meritv03_pref_talent 
pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw'

fitw02_c <- cfa(model = model03,data = dat01,estimator="MLR",std.lv=FALSE) # Continuous/ estimator ML Robust

fitw02_o <- cfa(model = model03,data = dat01,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                         "meritv03_perc_wpart","meritv03_perc_netw",
                                                         "meritv03_pref_effort","meritv03_pref_talent",
                                                         "meritv03_pref_wpart","meritv03_pref_netw"))
#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fitw02_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal= fitmeasures(fitw02_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fitw02_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                y = standardizedsolution(fitw02_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

> **NOTE**: El ajuste de muestra completa en wave 02 con estimator MLR (robusto) es bastante bueno (CFI, RMSEA). El ajuste con DWLS es bastante bueno, CFI mejora, RMSEA aumenta un poco (0.59). 

### Second order CFA

```{r}
modw2 <- '
perc_merit=~meritv03_perc_effort+meritv03_perc_talent 
perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw  
pref_merit=~meritv03_pref_effort+meritv03_pref_talent 
pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw 
merit =~perc_merit+pref_merit  
nmerit=~perc_nmerit+pref_nmerit'

# mod2_merit_c <- cfa(model = modw2,data = dat01) # Continuous/ estimator ML Robust

mod2_merit_o <- cfa(model = modw2,data = dat01,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                           "meritv03_perc_wpart","meritv03_perc_netw",
                                                           "meritv03_pref_effort","meritv03_pref_talent",
                                                           "meritv03_pref_wpart","meritv03_pref_netw"))

#---------------------------------------------------#
kable(rbind(Ordinal=fitmeasures(mod2_merit_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (DWLS)")
kable(standardizedsolution(mod2_merit_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
      format = "markdown",digits = 2,col.names = cnames)
```

<!-- > * Factor de segundo orden usando MLR no converge. -->
<!-- > * Factor de segundo orden usando DWLS converge, pero las cargas no son buenas y el ajuste tampoco. -->

> * Second order factor using MLR does not converge.
> * Second order factor using DWLS converges, but loads are not good and the fit is not.

# Summary fit indices wave 02

```{r}
sum_fitw02<- bind_rows(fitmeasures(fitw02a_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02a_o)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02b_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02b_o)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02c_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02c_c)[c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02_c)[ c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw02_o)[ c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],)

sum_fitw02$mod <- c("Model 1","Model 1","Model 2","Model 2","Model 3","Model 3","Model 4","Model 4")
sum_fitw02$est <- c("Continuous","Ordinal","Continuous","Ordinal","Continuous","Ordinal","Continuous","Ordinal")
sum_fitw02 <- select(sum_fitw02,mod,est,everything())

kable(sum_fitw02,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 02") %>% 
  kable_styling(full_width = F) %>% 
  collapse_rows(columns = 1,valign = "middle") %>% 
  footnote(number = c("Model 1: Control group sample", 
                      "Model 2: Poverty treatment condition sample",
                      "Model 3: Inequality treatment condition sample",
                      "Model 4: Complete sample"))
```

# Wave 03

```{r}
data03 <- sjlabelled::read_spss(path = "input/data/original/Estudio_3_ola3.sav",verbose = FALSE)
dat01 <- data03 %>% select(starts_with("meritv03_p")) 
```

```{r echo=TRUE,results='asis'}
stargazer(dat01,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```


```{r}
model03 <- '
perc_merit=~meritv03_perc_effort+meritv03_perc_talent 
perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw  
pref_merit=~meritv03_pref_effort+meritv03_pref_talent 
pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw'

fitw03c_c <- cfa(model = model03,data = dat01,estimator="MLR") # Continuous/ estimator ML Robust

fitw03c_o <- cfa(model = model03,data = dat01,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                          "meritv03_perc_wpart","meritv03_perc_netw",
                                                          "meritv03_pref_effort","meritv03_pref_talent",
                                                          "meritv03_pref_wpart","meritv03_pref_netw"))
#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fitw03c_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal= fitmeasures(fitw03c_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fitw03c_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                y = standardizedsolution(fitw03c_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```
**summary**

<!-- > * Ajuste usando estimator MLR  es bueno (CFI = 0.971, RMSEA = 0.052). El chi2 (robusto) es 62.421   -->
<!-- > * Ajuste usando estimator DWLS es bueno (CFI = 0.974, RMSEA = 0.067). El chi2 (robusto) es 106.111 -->

> * Adjustment using MLR estimator is good (CFI = 0.971, RMSEA = 0.052). The chi2 (robust) is 62,421
> * Fit using DWLS estimator is good (CFI = 0.974, RMSEA = 0.067). The chi2 (robust) is 106,111

# Summary fit indices wave 03 

```{r}
sum_fitw03<- bind_rows(fitmeasures(fitw03c_c)[ c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
                       fitmeasures(fitw03c_o)[ c("cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])

sum_fitw03$mod <- c("Model 1","Model 1")
sum_fitw03$est <- c("Continuous","Ordinal")
sum_fitw03 <- select(sum_fitw03,mod,est,everything())

kable(sum_fitw03,digits = 3,format = "html",row.names = F,booktabs=T,caption = "Summary fit indices wave 03") %>% 
  kable_styling(full_width = F) %>% 
  collapse_rows(columns = 1,valign = "middle") %>% 
  footnote(number = c("Model 1: Complete sample"))
```

